Case for Support

### 2021-11-16 application/trackRecord.tex
Cosmetic change

In summary, the partners in this project have outstanding expertise on their
focus areas (computational neuroscience and machine learning, experimental
neuroscience, implementation of experiments), as well as a rich collaborative
track record. The proposed project will merge the unique expertise of its
partner institutions to create a resource that will be essential for the
advanced of biological sciences.

>>>>

In summary, the partners in this project have outstanding expertise on their
focus areas (computational neuroscience and machine learning, experimental
neuroscience, implementation of experiments), as well as a rich collaborative
track record. The proposed project will merge this unique expertise to create a
resource that will be essential for the advanced of biological sciences.
